# Reproducible Research: Peer Assessment 1
===========================================

```{r setoptions,echo=FALSE}
opts_chunk$set(echo=TRUE)
```

## Loading and preprocessing the data

Downloda the raw data and read the data into Memory.
```{r}
act<-read.csv("D:/rprog-data-ProgAssignment3-data/activity.csv")
head(act,2)
```

Transform the date into date formate
```{r load}
act$date<-as.Date(act$date, format= "%Y-%m-%d")
class(act$date)
```


## What is mean total number of steps taken per day?

Make a histogram of the total number of steps taken each day
```{r echo=FALSE,results='hide'}
Sys.setlocale("LC_TIME", "English")
```
```{r fig.width=8, fig.height=4}
plot(unique(act[!is.na(act$steps),"date"])
     ,tapply(act[!is.na(act$steps),"steps"],act[!is.na(act$steps),"date"],sum)
     ,type="h",main="Total Number of Steps",ylab="Number of Steps",xlab=NA)
```

Calculate and report the mean and median total number of steps taken per day
```{r}
library("plyr")
a<-ddply(act,.(date),summarize,
         mean=mean(steps,na.rm=TRUE),
         median=median(steps,na.rm=TRUE))
print(a)
```



## What is the average daily activity pattern?
```{r fig.width=8,fig.height=4}
library(plyr)
meanInterval<-ddply(act,.(interval),summarize,
               mean=mean(steps,na.rm=TRUE))
maxInterval<-meanInterval[which.max(meanInterval$mean),][1]
print(paste("On average across all the days,the",maxInterval,
            "interval contains the maximum number of steps",sep=" "))
plot(meanInterval$interval,meanInterval$mean,type = "l",
     xlab="interval",ylab="number of steps",main="Average Daily Activity Pattern")
```

## Imputing missing values
Calculate and report the total number of missing values in the dataset
```{r}
nasNum<-sum(is.na(act$steps))
print(paste("The total number of rows with NAs is",nasNum,sep=" "))
```
Create a new dataset without missing values
```{r, cache=TRUE}
actnona<-act[c("date","interval")]
for(i in 1:nrow(actnona)){
        if(is.na(act$steps[i])){
                actnona$steps[i]<-meanInterval[meanInterval[1]==act[i,"interval"],2]
        }
        else actnona$steps[i]<-act$steps[i]
}
head(actnona,2)
```
Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r echo=FALSE, results='hide'}
Sys.setlocale("LC_TIME", "English")
```
```{r fig.width=8,fig.height=4}
plot(unique(actnona[!is.na(actnona$steps),"date"])
     ,tapply(actnona[!is.na(actnona$steps),"steps"],
             actnona[!is.na(actnona$steps),"date"],sum,na.rm=TRUE)
     ,type="h",main="Total Number of Steps(missing values were imputed)",
     xlab=NA,ylab="Number of Steps"
     )
```
Calculate and report the mean and median total number of steps taken per day
```{r}
library(plyr)
a<-ddply(actnona,.(date),summarize,
         mean=mean(steps,na.rm=TRUE),
         median=median(steps,na.rm=TRUE))
print(a)
```
The shape of the distributione is't change,but the more missing valuse,the more sparse lines 
```{r, echo=FALSE,results='hide'}
Sys.setlocale("LC_TIME", "English")
```
```{r fig.width=10,fig.height=4}
par(mfcol=c(1,2))
plot(unique(actnona[!is.na(actnona$steps),"date"])
     ,tapply(actnona[!is.na(actnona$steps),"steps"],
             actnona[!is.na(actnona$steps),"date"],sum)
     ,type="h",main="Total Number of Steps(missing values were imputed)",
     xlab=NA,ylab="Number of Steps"
)
plot(unique(act[!is.na(act$steps),"date"])
     ,tapply(act[!is.na(act$steps),"steps"],
             act[!is.na(act$steps),"date"],sum)
     ,type="h",main="Total Number of Steps(include missing data)",
     xlab=NA,ylab=NA
)
```



## Are there differences in activity patterns between weekdays and weekends?
Create a new factor variable in the dataset with two levels "weekday" and "weekend"
```{r, echo=FALSE,results='hide'}
Sys.setlocale("LC_TIME", "English")
```
```{r}
actnona$weekdays<-ifelse(
        weekdays(actnona$date)=="Saturday"|weekdays(actnona$date)=="Sunday"
        ,"weekend","weekday")
actnona$weekdays<-factor(actnona$weekdays)
```
Make a panel plot of the interval and the average number of steps taken
```{r, fig.height=6,fig.width=8}
library(plyr)
actnonaInterval<-ddply(actnona,.(interval,weekdays),summarize,mean=mean(steps))
library("ggplot2")
ggplot(actnonaInterval,aes(x=interval,y=mean))+
        geom_line(colour="green")+
        facet_grid(weekdays~.)+
        labs(title="Activity Patterns",x="Interval",y="Number of steps")+
        theme_bw(base_family = "Times")
```